---
title: "Sean Conner resume"
author: Sean Conner
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
    css:
      - custom_resume.css
# uncomment this line to produce HTML and PDF in RStudio:
#knit: pagedown::chrome_print
---


Aside
================================================================================
```{r include = F}

library(magick)

hs_path <- "images/Close.jpg"

hs_read <- magick::image_read(hs_path)

hs_info <- magick::image_info(hs_read)

hs_mins <- min(hs_info$width, hs_info$height)

hs_crop <- magick::image_crop(hs_read, geometry = paste0(hs_mins, "x", hs_mins, "+400+0"), repage = T)

new_bg <- magick::image_draw(magick::image_blank(hs_mins, hs_mins))
symbols(hs_mins/2, hs_mins/2, circles=(hs_mins/2)-3, bg='black', inches=FALSE, add=TRUE)
dev.off()

hs_bg_composite <- magick::image_composite(hs_crop, new_bg, operator='copyopacity')

final_circular_hs <- magick::image_background(hs_bg_composite, '#f5f8fc')

magick::image_write(final_circular_hs, "images/Close_Circular.jpg")

```
Contact Info {#contact}
--------------------------------------------------------------------------------

- <i class="fa fa-envelope"></i> scconner7@gmail.com
- <i class="fa fa-github"></i> [github.com/Lydisis](https://github.com/Lydisis)
- <i class="fa fa-phone"></i> +1 601-490-5086
- For more information, please contact me via email.

<i class="fa fa-laptop"></i> Data Analytics Skills {#skills}
--------------------------------------------------------------------------------

```{r, message=F, warning=F, echo = F, fig.height=14, fig.width=18}

library(tidyverse)

technical_skill_bar_data <- tibble(skills = c("R", "SQL", "Tableau", "Git", "Python"),
                         levels = c(8, 7, 7, 6, 4))


# technical_skill_bar_data %>% 
#   ggplot(aes(x = levels, y = fct_rev(fct_reorder2(skills, skills, levels)))) +
#   geom_bar(fill = "#ffe6e8", aes(x = 8), stat = "identity", color = "light gray", size = 1)+
#   geom_bar(fill = "navy blue", stat = "identity", color = "light gray", size = 0.75)+
#   theme_classic()+
#   theme(axis.title = element_blank(),
#         axis.ticks = element_blank(),
#         axis.line = element_blank(),
#         axis.text.x = element_blank(),
#         axis.text.y = element_text(margin = margin(0,-15,0,0),
#                                    size = 80,
#                                    face = "bold",
#                                    color = "#737373"),
#         plot.background = element_rect(fill = "#f5f8fc"),
#         panel.background = element_rect(fill = "#f5f8fc"))

create_skill_bar_data <-
  function(max_skill_level,
           skill_names,
           skill_levels) {
    
    skill_col <- function(skill_names, max_skill_level) {
      skill_names %>%
        map( ~ rep(.x, max_skill_level)) %>%
        reduce(c)
    }
    
    df <- data.frame(skill = skill_col(skill_names, max_skill_level))
    
    max_level_col <- function(max_skill_level, skill_names) {
      rep(1:max_skill_level, length(skill_names))
    }
    
    df <- df %>%
      mutate(max_level = max_level_col(max_skill_level, skill_names))
    
    skill_level_col <- function(skill_levels, max_skill_level) {
      skill_levels %>%
        map( ~ c(rep("Fill", .x), rep("Empty", max_skill_level - .x))) %>%
        reduce(c)
    }
    
    df <- df %>%
      mutate(skill_level = skill_level_col(skill_levels, max_skill_level))
    
    df
  }

test <- create_skill_bar_data(5, c("R", "SQL", "Tableau", "Git", "Python"), c(5, 4, 4, 3, 2))

# test <-
#   tibble(
#     skill = c(
#       rep("R", 5),
#       rep("SQL", 5),
#       rep("Tableau", 5),
#       rep("Git", 5),
#       rep("Python", 5)
#     ),
#     max_level = c(1:5, 1:5, 1:5, 1:5, 1:5),
#     skill_level = c(
#       rep("Fill", 5),
#       rep("Fill", 4),
#       "Empty",
#       rep("Fill", 4),
#       "Empty",
#       rep("Fill", 4),
#       "Empty",
#       rep("Fill", 4),
#       "Empty"
#     )
#   )

test %>% 
  ggplot()+
  geom_point(aes(x = max_level, y = fct_rev(fct_inorder(skill)), color = skill_level), size = 40)+
  geom_hline(yintercept = c(seq(1.5, 4.5, by = 1)), color = "#ffe6e8", linetype = 2, size = 5)+
  geom_segment(color = "#ffe6e8", linetype = 2, y = 1.5, yend = 1.5, x = -1, xend = 0.76, size = 5)+
  geom_segment(color = "#ffe6e8", linetype = 2, y = 2.5, yend = 2.5, x = -1, xend = 0.76, size = 5)+
  geom_segment(color = "#ffe6e8", linetype = 2, y = 3.5, yend = 3.5, x = -1, xend = 0.76, size = 5)+
  geom_segment(color = "#ffe6e8", linetype = 2, y = 4.5, yend = 4.5, x = -1, xend = 0.76, size = 5)+
  coord_cartesian(xlim = c(1, 5), clip = "off")+
  scale_color_manual(values = c("light gray", "navy"))+
  theme(axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_text(margin = margin(0,10,0,0),
                                   size = 80,
                                   face = "bold",
                                   color = "#737373",
                                   hjust = 0),
        plot.background = element_rect(fill = "#f5f8fc"),
        panel.background = element_rect(fill = "#f5f8fc"),
        legend.position = "none")

```

<i class="fa fa-users"></i> Interpersonal Skills {#skills}
--------------------------------------------------------------------------------

```{r, message=F, warning=F, echo = F, fig.height=14, fig.width=18}

library(tidyverse)

skill_bar_data <- tibble(skills = c("R", "SQL", "Tableau", "Git", "Python"),
                         levels = c(8, 7, 7, 6, 4))


skill_bar_data %>% 
  ggplot(aes(x = levels, y = fct_rev(fct_reorder2(skills, skills, levels)))) +
  geom_bar(fill = "#ffe6e8", aes(x = 8), stat = "identity", color = "light gray", size = 1)+
  geom_bar(fill = "navy blue", stat = "identity", color = "light gray", size = 0.75)+
  theme_classic()+
  theme(axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_text(margin = margin(0,-15,0,0),
                                   size = 80,
                                   face = "bold",
                                   color = "#737373"),
        plot.background = element_rect(fill = "#f5f8fc"),
        panel.background = element_rect(fill = "#f5f8fc"))

```

Disclaimer {#disclaimer style="width: var(--sidebar-width); padding-left: var(--sidebar-horizontal-padding);"}
--------------------------------------------------------------------------------

This resume was made with the R package [**pagedown**](https://github.com/rstudio/pagedown).
My customized code used to produce it can be found on my GitLab [**here**]().
Last updated on `r Sys.Date()`.

Main
================================================================================

Sean Conner {#title}
--------------------------------------------------------------------------------

### Currently searching for a Data Scientist position

Some stuff here?

### Skills
<style>
div.flex-child {
flex: 0 1 auto;
background-color: #eff3ff;
border: 1px solid #d9d9d9;
border-radius: 5px;
box-sizing: border-box;
margin: 3px;
padding: 2px 5px 2px 5px;
max-height: 30px;
align-self: center;
}
</style>

<div style="display: flex; flex-wrap: wrap; max-width: 750px; padding: 3px; white-space: nowrap; align-items: center"; justify-content: center>
<div class="flex-child">
Data Visualization
</div>

<div class="flex-child">
Statistical Analysis
</div>

<div class="flex-child">
Regression
</div>

<div class="flex-child">
Data Cleaning
</div>

<div class="flex-child">
Writing
</div>

<div class="flex-child">
Shiny
</div>

<div class="flex-child">
R Markdown
</div>

<div class="flex-child">
Business Intelligence
</div>

</div>



Professional Experience {data-icon=laptop}
--------------------------------------------------------------------------------

### Solutions Engineer 

Green Mountain Technology

Remote full-time

Present - Aug. 2020

- Work daily with large, complex datasets to create automated report pipelines and business intelligence dashboards using combinations of SQL, R / RMarkdown, Shiny, Excel, and Tableau.
- Conduct *ad hoc* strategic analyses of parcel shipping networks for multiple Fortune 100 companies, such as request for proposal (RFP) evaluations and network optimizations.
- Led operations-wide roll-out of Git & GitLab with self-authored tutorial documents and live demos.
- Summarize and present *ad hoc*, weekly, and monthly analyses to audiences up to senior VP-level executives of Fortune 100 companies.
- Lead weekly engineer alignment meetings to share methods and standardize work.


### Research Associate

MSU - John C. Stennis Institute of Government

Starkville, MS

Aug. 2020 - Aug. 2019

- Conducted factor analysis and regression modeling of state agencies’ employee engagement and turnover intention.
- Presented results to state agency executives, academic conferences, and local-level elected officials.
- Served as principal investigator (PI) on three survey projects.
- Served as Co-PI on a comprehensive program inventory report of education, health, and safety programs provided to K-12 children in MS for the state auditor's office.


### Graduate Research Assistant

MSU - John C. Stennis Institute of Government

Starkville, MS

Aug. 2019 - July 2017

- Created Shiny web applications to clearly visualize customizable reports requested by stakeholders.
- Performed event-history / survival analyses to project jurisdictions’ policy adoption likelihoods.
- Presented academic research projects and attended interactive workshops at conferences around the country.


### Graduate Teaching Assistant

MSU - Communications Dept.

Starkville, MS

May 2017 - Aug 2016

-	Taught students to shoot and edit television-quality video and audio.
-	Prepared lectures, graded assignments, and provided technical assistance to students.


### Technical Intern

MS Legislative PEER Committee

Jackson, MS

April 2014 - Jan. 2014

-	Collected and cataloged program inventory data from county-regional and private prison facilities across the state for the Pew-MacArthur Results First Initiative, a comprehensive cost-benefit analysis of government programs across the country.
- Provided legislative briefs and data visualizations to committee members.
- Assisted with survey questionnaire construction, sampling, and presentations of finding.


Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

### Mississippi State University (MSU)

Ph.D - Public Policy and Administration

Starkville, MS

Present (anticipated graduation Fall 2023)

GPA 4.00 / 4.00


### MSU

Master of Public Policy and Administration (MPPA)

Starkville, MS

Aug. 2018 - Aug. 2016

GPA 4.00 / 4.00


### University of Mississippi

Bachelor of Arts in Political Science

Oxford, MS

Aug. 2015 - Aug. 2010

GPA 3.34 / 4.00



Leadership & Awards {data-icon=medal data-concise=true}
--------------------------------------------------------------------------------

### MSU

Student

Starkville, MS

- Voted Outstanding Graduate Student by faculty (2018).
- Student Representative for MPPA program (September 2017 – May 2018).
- Graduate Student Advisor to Stennis-Montgomery Association, a student organization promoting civic engagement (2018).
- The Honor Society of Phi Kappa Phi (2017-2018).
- Awarded cash prize for best graduate student presentation at MS Political Science Association Conference (2018).


### University of MS

Student

Oxford, MS

- Dean’s List (four semesters).
- Represented UM at the National Model UN in NYC (2010).
- Pi Sigma Alpha, the Political Science Honors Society (2014-2015).
- Provost Scholar (2010-2015).
- Elected President of the Senate for UM Model Senate (Fall 2013).




 
