---
title: "Sean Conner resume"
author: Sean Conner
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
    css:
      - custom_resume.css
# uncomment this line to produce HTML and PDF in RStudio:
#knit: pagedown::chrome_print
---

```{r setup, include = F}

library(tidyverse)

```


Aside
================================================================================

Contact Info {#contact}
--------------------------------------------------------------------------------
- <i class="fa fa-envelope"></i> scconner7@gmail.com
- <i class="fa fa-phone"></i> +1 601-490-5086
- <i class="fa fa-github"></i> [github.com/scconner7](https://github.com/scconner7)


<i class="fa fa-toolbox"></i> Languages and Tools {#languages}
--------------------------------------------------------------------------------
```{r, message=F, warning=F, echo = F, fig.height=14, fig.width=18}

create_skill_bar_data <-
  function(max_skill_level,
           skill_names,
           skill_levels) {
    skill_col <- function(skill_names, max_skill_level) {
      skill_names %>%
        map(~ rep(.x, max_skill_level)) %>%
        reduce(c)
    }
    
    df <-
      data.frame(skill = skill_col(skill_names, max_skill_level))
    
    max_level_col <- function(max_skill_level, skill_names) {
      rep(1:max_skill_level, length(skill_names))
    }
    
    df <- df %>%
      mutate(max_level = max_level_col(max_skill_level, skill_names))
    
    skill_level_col <- function(skill_levels, max_skill_level) {
      skill_levels %>%
        map(~ c(rep("Fill", .x), rep("Empty", max_skill_level - .x))) %>%
        reduce(c)
    }
    
    df <- df %>%
      mutate(skill_level = skill_level_col(skill_levels, max_skill_level))
    
    df
  }

skill_dots_data <-
  create_skill_bar_data(5,
                        c("R", "SQL", "Tableau", "Git", "HTML", "CSS", "Python"),
                        c(5, 4, 4, 4, 3, 3, 2))



skill_dots_data %>%
  ggplot() +
  geom_point(aes(
    x = max_level,
    y = fct_rev(fct_inorder(skill)),
    color = skill_level
  ), size = 40) +
  geom_hline(
    yintercept = c(seq(1.5, 6.5, by = 1)),
    color = "#ffe6e8",
    linetype = 2,
    size = 5
  ) +
  geom_segment(
    color = "#ffe6e8",
    linetype = 2,
    y = 1.5,
    yend = 1.5,
    x = -1,
    xend = 0.76,
    size = 5
  ) +
  geom_segment(
    color = "#ffe6e8",
    linetype = 2,
    y = 2.5,
    yend = 2.5,
    x = -1,
    xend = 0.76,
    size = 5
  ) +
  geom_segment(
    color = "#ffe6e8",
    linetype = 2,
    y = 3.5,
    yend = 3.5,
    x = -1,
    xend = 0.76,
    size = 5
  ) +
  geom_segment(
    color = "#ffe6e8",
    linetype = 2,
    y = 4.5,
    yend = 4.5,
    x = -1,
    xend = 0.76,
    size = 5
  ) +
  geom_segment(
    color = "#ffe6e8",
    linetype = 2,
    y = 5.5,
    yend = 5.5,
    x = -1,
    xend = 0.76,
    size = 5
  ) +
  geom_segment(
    color = "#ffe6e8",
    linetype = 2,
    y = 6.5,
    yend = 6.5,
    x = -1,
    xend = 0.76,
    size = 5
  ) +
  coord_cartesian(xlim = c(1, 5), clip = "off") +
  scale_color_manual(values = c("light gray", "navy")) +
  theme(
    axis.title = element_blank(),
    axis.ticks = element_blank(),
    axis.line = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(
      margin = margin(0, 10, 0, 0),
      size = 80,
      face = "bold",
      color = "#737373",
      hjust = 0
    ),
    plot.background = element_rect(fill = "#f5f8fc"),
    panel.background = element_rect(fill = "#f5f8fc"),
    legend.position = "none"
  )

```


<i class="fa fa-certificate"></i> Certifications {#certs}
--------------------------------------------------------------------------------
- IBM Data Science Fundamentals Specialization ([verification link](https://www.credly.com/badges/5269971e-1d74-4273-8115-072d18b88e05?source=linked_in_profile))


<i class="fa fa-laptop"></i> Skills {#skills}
--------------------------------------------------------------------------------
<style>
div.flex-child {
flex: 0 1 auto;
background-color: #eff3ff;
border: 1px solid #d9d9d9;
border-radius: 5px;
box-sizing: border-box;
margin: 3px;
padding: 2px 5px 2px 5px;
max-height: 30px;
align-self: center;
}
</style>


<div style="display: flex; flex-wrap: wrap; max-width: 750px; padding: 3px; white-space: nowrap; align-items: center"; justify-content: center>

<div class="flex-child">
Data Visualization
</div>

<div class="flex-child">
Shiny
</div>

<div class="flex-child">
Writing
</div>

<div class="flex-child">
Statistical Analysis
</div>

<div class="flex-child">
Regression Modeling
</div>

<div class="flex-child">
Data Cleaning
</div>

<div class="flex-child">
R Markdown
</div>

<div class="flex-child">
R tidyverse
</div>

<div class="flex-child">
Business Intelligence
</div>

<div class="flex-child">
Survey Design
</div>

<div class="flex-child">
Microsoft Office
</div>

<div class="flex-child">
GitHub / GitLab
</div>

<div class="flex-child">
Time-Series
</div>

<div class="flex-child">
Atlassian Cloud
</div>

<div class="flex-child">
R Package Development
</div>

<div class="flex-child">
Data Warehousing
</div>

<div class="flex-child">
Econometrics
</div>

<div class="flex-child">
Event-History Analysis
</div>

<div class="flex-child">
Machine Learning
</div>

</div>


Disclaimer {#disclaimer style="width: var(--sidebar-width); padding-left: var(--sidebar-horizontal-padding);"}
--------------------------------------------------------------------------------
This resume was made with the R package [**pagedown**](https://github.com/rstudio/pagedown).<br></br>
Code available on my GitHub [**here**](https://github.com/scconner7/Pagedown-Resume).<br></br>
Last updated on `r Sys.Date()`.


Main
================================================================================

Sean Conner {#title}
--------------------------------------------------------------------------------
### Currently searching for a Data Scientist position



Professional Experience {data-icon=laptop}
--------------------------------------------------------------------------------

### Solutions Engineer 

Green Mountain Technology

Remote full-time

Present - Aug. 2020

- Conduct *ad hoc* strategic analyses of parcel shipping networks for multiple Fortune 100 companies, such as request for proposal (RFP) evaluations and network optimizations.
- Work daily with large, complex datasets to create automated report pipelines and business intelligence dashboards using combinations of SQL, R / RMarkdown, Shiny, Excel, and Tableau.
- Summarize and present *ad hoc*, weekly, and monthly analyses to audiences up to senior VP-level executives of Fortune 100 companies.
- Developed and maintain an internal R package for the modularization of strategic analyses, creation / database upload of net rate matrices, and bulk, cross-customer exception management.
- Led operations-wide roll-out of Git & GitLab with self-authored tutorial documents and live demos.
- Lead weekly engineer alignment meetings to share methods and standardize work.


### Research Associate

MSU - John C. Stennis Institute of Government

Starkville, MS

Aug. 2020 - Aug. 2019

- Conducted factor analysis and regression modeling of state agencies’ employee engagement and turnover intention.
- Presented results to state agency executives, academic conferences, and local-level elected officials.
- Served as principal investigator (PI) on three survey projects.
- Served as Co-PI on a comprehensive program inventory report of education, health, and safety programs provided to K-12 children in MS for the state auditor's office.


### Graduate Research Assistant

MSU - John C. Stennis Institute of Government

Starkville, MS

Aug. 2019 - July 2017

- Created Shiny web applications to clearly visualize customizable reports requested by stakeholders.
- Performed event-history / survival analyses to estimate jurisdictions’ policy adoption likelihoods.
- Presented academic research projects and attended interactive workshops at conferences around the country.


### Graduate Teaching Assistant

MSU - Communications Dept.

Starkville, MS

May 2017 - Aug 2016

-	Taught students to record television-quality video and audio and edit both with Adobe Premiere.


### Technical Intern

MS Legislative PEER Committee

Jackson, MS

April 2014 - Jan. 2014

-	Collected and cataloged program inventory data from county-regional and private prison facilities across the state for the Pew-MacArthur Results First Initiative, a comprehensive cost-benefit analysis of government programs across the country.
- Provided legislative briefs and data visualizations to committee members.
- Assisted with survey questionnaire construction, sampling, and presentations of finding.


Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

### Mississippi State University (MSU)

Ph.D - Public Policy and Administration

Starkville, MS

Present (anticipated graduation Fall 2023)

GPA 4.00 / 4.00


### MSU

Master of Public Policy and Administration (MPPA)

Starkville, MS

Aug. 2018 - Aug. 2016

GPA 4.00 / 4.00


### University of Mississippi (UM)

Bachelor of Arts in Political Science

Oxford, MS

Aug. 2015 - Aug. 2010

GPA 3.34 / 4.00


Leadership & Awards {data-icon=medal data-concise=true}
--------------------------------------------------------------------------------

### MSU

Student

Starkville, MS

- Voted Outstanding Graduate Student by faculty (2018).
- Student Representative for MPPA program (September 2017 – May 2018).
- Graduate Student Advisor to Stennis-Montgomery Association, a student organization promoting civic engagement (2018).
- The Honor Society of Phi Kappa Phi (2017-2018).
- Awarded cash prize for best graduate student presentation at MS Political Science Association Conference (2018).


### UM

Student

Oxford, MS

- Dean’s List (four semesters).
- Represented UM at the National Model UN in NYC (2010).
- Pi Sigma Alpha, the Political Science Honors Society (2014-2015).
- Provost Scholar (2010-2015).
- Elected President of the Senate for UM Model Senate (Fall 2013).




 
